\documentclass[centered,margin, 11pt]{cv}

\usepackage{upgreek} % For upright Greek letters.
%\renewcommand{\title}[1]{\bf {#1}} 
\author{Christopher K. Black}
\address{ 
Institute for Genomic Biology, University of Illinois\\
Room 1500\\
1206 W. Gregory Drive, Urbana, IL 61801\\
(503) 929\textendash 9421\\
black11@illinois.edu
}

\begin{document}
\maketitle
\begin{resume}

%\section{Research Interests}
%Plant biology. Special interest in the mechanisms and ecology of trophic %interactions between plants and other organisms.
%
%Carbon cycling
%root development
%ecophysiology
%Effects of global change on plant ecophysiology


\section{Education}
Ph.D. in progress, Plant Biology. University of Illinois, completion expected 2015.\\ 
B.A., Biology. Reed College 2008. 


\section{Papers and Presentations}
{\bf Black, C.}, Davis, S.C., Bernacchi, C.J., DeLucia, E.H. ``Response of soil respiration to ecosystem warming and elevated atmospheric carbon dioxide.'' Poster presented at the Ecological Society of America annual meeting, August 2010.  

{\bf Black, C.} 2008. \textit{Associative Nitrogen Fixation Ability Does Not Predict Symbiotic Nodulation Ability in} Burkholderia tropica. Reed College thesis.

Lin, R., Teng, Y., Park, H.J., Ding, L., {\bf Black, C.}, Fang, P., Wang, H. 2008. Discrete and Essential Roles of the Multiple Domains of Arabidopsis FHY3 in Mediating Phytochrome A Signal Transduction. \textit{Plant Physiology} 148: 981-992.

``Functional significance of conserved amino acids for light signaling in FHY3.'' Talk given at the Boyce Thompson Institute summer student research symposium. August 2007.

	

\section{Honors and Awards}
{\bf Internship in Plant Genomics} at Boyce Thompson Institute, supported by NSF Research Experience for Undergraduates grant DBIÐ0453331, 2007.\\
{\bf Thesis research} supported by a grant to Reed College from the James F. and Marion L. Miller Foundation, 2007-2008.\\
{\bf Undergraduate research} supported by a grant to Reed College from the James F. and Marion L. Miller Foundation, 2006.\\
{\bf Faculty commendation} for academic excellence, Reed College 2004-2005.


\section{Work History}
    
    \title{Research Assistant}
    \employer{University of Illinois}
    \location{Urbana, IL}
    \dates{2009-present}
    \begin{position}
    \end{position}
    
    \title{Research Assistant}
    \employer{Energy Biosciences Institute}
    \location{Urbana, IL}
    \dates{2009}
    \begin{position}
    \end{position}

	\title{Arborist} 
	\employer{Rich's Tree Service}
	\location{Fairview, OR} 
	\dates{2008 \textendash\ 2009}	
	\begin{position}
	\end{position}		
	
	\title{Plant Genomics Research Intern} 
	\employer{Boyce Thompson Institute}
	\location{Ithaca, NY} 
	\dates{2007}	
	\begin{position}
	\end{position}	

	\title{Multimedia Lab Assistant} 
	\employer{Reed College}
	\location{Portland, OR} 
	\dates{2004 \textendash\ 2007}	
	\begin{position}
	\end{position}		
 
	\title{Landscape Maintenance Crewman} 
	\employer{Ascent Tree and Yard Care}
	\location{Portland, OR} 
	\dates{2003 \textendash\ 2005}	
	\begin{position}
	\end{position}	

	\title{Water-pumping Windmill Repairman} 
	\employer{LoTec Windmill Service}
	\location{Arkansaw, WI} 
	\dates{1989 \textendash\ 2004}	
	\begin{position}
	\end{position}	
	
	\title{Junior Staff} 
	\employer{Not Back To School Camp}
	\location{Bridge, OR} 
	\dates{2002}	
	\begin{position}
	\end{position}


	\title{Historical Carpentry Intern} 
	\employer{George Washington's Mount Vernon}
	\location{Mount Vernon, VA} 
	\dates{2001}	
	\begin{position}
	\end{position}	

	\title{Junior Staff} 
	\employer{Camp Woodbrook}
	\location{Richland Center, WI} 
	\dates{2000}	
	\begin{position}
	\end{position}
	
\section{Volunteer work}
	\title{Historical carpentry demonstrator} 
	\employer{Fort Vancouver}
	\location{Vancouver, WA} 
	\dates{2003 \textendash\ 2004}	
	\begin{position}
	\end{position}	

\section{Skills and Qualifications}
	{\sc Lab}: Experience with PCR, bacterial cloning, spectrophotometry, IRGA, gas and liquid chromatography, bacteriophage isolation, sterile plant and bacterial culture, {\it Arabidopsis} and legume growth.\\
{\sc Field}: Experience with soil respiration measurements, minirhizotron imaging, plant identification, survey methods, breeding techniques, tree climbing, working outdoors in all weathers. Background in gardening, arboriculture, camping, climbing, construction.\\
{\sc Computer}: Proficient Mac OS X and Linux systems administrator. Experience with LaTeX, R statistics package, BLAST, ImageJ, Excel, Photoshop, Illustrator, Python, PHP, C, Scheme, SQL.\\

\end{resume}
\end{document}