\documentclass[centered,margin, 11pt]{resume}

\usepackage{upgreek} % For upright Greek letters.
%\renewcommand{\title}[1]{\bf {#1}} 
\title{CV}
\author{Christopher K. Black\\
black11@illinois.edu\\
(503) 929\textendash 9421\\
Institute for Genomic Biology, University of Illinois\\
1206 W. Gregory Drive, Room 1500\\
Urbana, IL 61801}

\begin{document}
\maketitle

\section{Education}
Reed College, B.A. Biology 2008.\\
University of Illinois, Ph.D. Plant Biology expected 2013. 

\section{Interests}
Ecology, microbiology, and biogeochemistry of below-ground plant-environment interactions. Special interests in commensal and mutualistic trophic exchanges, responses to abiotic conditions, and nutrient storage.

\section{Publications and Presentations}
\begin{itemize}
	\item{{\bf Black, C.K.}, Davis, S.C., Bernacchi, C.J., DeLucia E.H. \textit{Ecosystem warming alters heterotrophic but not total soil respiration at SoyFACE}. Poster at INTERFACE workshop 2011, Captiva, FL.}
	\item{{\bf Black, C.K.}, Davis, S.C., Bernacchi, C.J., DeLucia E.H. \textit{Response of soil respiration to ecosystem warming and elevated atmospheric carbon dioxide}. Poster at Ecological Society of America annual meeting 2010, Pittsburgh, PA.}
	\item{{\bf Black, C.} 2008. \textit{Associative Nitrogen Fixation Ability Does Not Predict Symbiotic Nodulation Ability in} Burkholderia tropica. Reed College thesis.}
	\item{Lin, R., Teng, Y., Park, H.J., Ding, L., {\bf Black, C.}, Fang, P., Wang, H. 2008. Discrete and Essential Roles of the Multiple Domains of Arabidopsis FHY3 in Mediating Phytochrome A Signal Transduction. \textit{Plant Physiology} 148: 981-992.}
\end{itemize}


\section{Research projects}
\begin{itemize}
	\item{Model parameterization for predicting soil carbon dynamics under altered future climate conditions. University of Illinois, 2010-present.}
	\item{Isotopic partitioning of root and microbe components of soil respiration. University of Illinois, 2010-present.}
	\item{Soil respiration, microbial genomics, and carbon cycling of an experimentally heated corn-soy ecosystem. University of Illinois, 2009-present.}
	\item{Root distribution, below-ground biomass, and water usage of potential biofuels crops. University of Illinois, 2009-present.}
	\item{Host range of N-fixing microbes. Undergraduate thesis work, Reed College, 2007-2008.}
	\item{Genetics of light signaling in Arabidopsis. NSF-REU internship, Boyce Thompson Institute/Cornell, 2007.}
\end{itemize}


	
\section{Professional memberships}
	Ecological Society of America. 2010-present. 	
\section{Other activities}
	University of Illinois Bio-Outreach. Introducing high school students to university biology research. 2010-present.
	
\section{References}
	
	Dr. Evan H. DeLucia, doctoral advisor. delucia@life.uiuc.edu, (217) 333-6177\\
	Dr. Carl J. Bernacchi. bernacch@uiuc.edu, (217) 333-8048\\
	Dr. Andrew Leakey. leakey@uiuc.edu, (217) 244-0302

\end{document}